The backbone of the team, providing outreach and media content to further enrich our teams' presence both internally and with other teams. Team 1280's Business subteam launched various operations to obtain funds and outreach events that teach our youth and inspire a passion for STEAM. 
\subheading{Business/Media}
During the year of 2024, the business and media team launched a various of social media posts for Tiktok and Instagram, getting over 2,000 natural impression, to encourage Students to partake in robotics Activities. Our Social Media posts have also gained us the attentions and great friendships with various teams. In one case, it has even given us valued team members and mentors. In our pursual of fundrasising, anticipating our influx of mentors, we applied for several grents, inclufing and most importantly the Gene Haas Foundation and Lawrence Livermore Labs. Similarly, we have fundraised with companies like Chipotle and Panda Express. Even without monetary compensation, Team 1280's Business has arranged an array of various outreach events with all sorts of groups, trying to inspire the STEM mindset in people both young and old. This year, buisness has arranged a trip to our local veterans' center, Vista Grande Elementry School's STEM Night, and even partnered with our school's AP Environmental Scinces class to arrange out annual E-Waste drive in order to ethicall dispose of electronic waste that often gets disposed of improperly.  
\subheading{Outreach}
Team 1280 is all about outreach during the off season. During this Off Season, Team 1280 has attended 4 outreach events, including 
